\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{// All comments are NOT created equal}

### 2015-05-17 paper/paper.tex
tiny change
improving distance

\usepackage{titlesec} % Allows customization of titles
%\renewcommand\thesection{\Roman{section}} % Roman numerals for the sections
%\renewcommand\thesubsection{\Roman{subsection}} % Roman numerals for subsections
\titleformat{\section}[block]{\large\scshape\centering\bfseries}{\thesection.}{1em}{} % Change the look of the section titles
\titleformat{\subsection}[block]{\large\scshape}{\thesubsection.}{1em}{} % Change the look of the section titles
\usepackage{cite}
\usepackage{fancyhdr} % Headers and footers
\pagestyle{fancy} % All pages have headers and footers
\fancyhead{} % Blank out the default header
\fancyfoot{} % Blank out the default footer
\fancyhead[C]{Naomi Pentrel $\cdot$ \href{mailto:n.pentrel@jacobs-university.de}{n.pentrel@jacobs-university.de} $\cdot$ \today} % Custom header text
\fancyfoot[RO,LE]{\thepage} % Custom footer text
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage[]{natbib}
\usepackage{tocloft}
\renewcommand*{\figureautorefname}{figure}
\def\stex{\texorpdfstring{\raisebox{-.5ex}S\kern-.5ex\TeX}{sTeX}\xspace}
\def\sTeX{\stex}

@@

\vspace*{4cm}

@@

\subsection{Distance Between Robot and Reef}

\begin{wrapfigure}{l}{0.27\textwidth}
\vspace{-28pt}
  \begin{center}
  \fbox{
    \includegraphics[width=0.25 \textwidth]{assets/reefSideways.jpg}
    }
  \end{center}
\vspace{-20pt}
  \caption{Reef Sideways}
  \label{fig:reef}
\vspace{20pt}
\end{wrapfigure}

@@

\begin{wrapfigure}{c}{\textwidth}
\vspace{-28pt}
  \begin{center}
  \fbox{
    \includegraphics[width=0.47 \textwidth]{assets/MapOnlyDistance}
    \includegraphics[width=0.4015 \textwidth]{assets/reefOriginalMappedComp}
    }
  \end{center}
\vspace{-20pt}
  \caption{Mapping using the Distance Algorithm}
  \label{fig:firstMapping}
\vspace{20pt}
\end{wrapfigure}

@@

\subsection{Fixing holes}
\ednote{more sensors or looking left and right}

>>>>

\usepackage{titlesec} % Allows customization of titles
%\renewcommand\thesection{\Roman{section}} % Roman numerals for the sections
%\renewcommand\thesubsection{\Roman{subsection}} % Roman numerals for subsections
\titleformat{\section}[block]{\large\scshape\centering\bfseries}{\thesection.}{1em}{} % Change the look of the section titles
\titleformat{\subsection}[block]{\large\scshape}{\thesubsection.}{1em}{} % Change the look of the section titles
\usepackage{cite}
\usepackage{fancyhdr} % Headers and footers
\pagestyle{fancy} % All pages have headers and footers
\fancyhead{} % Blank out the default header
\fancyfoot{} % Blank out the default footer
\fancyhead[C]{\href{mailto:n.pentrel@jacobs-university.de}{Naomi Pentrel} $\cdot$ \href{d.rochau@jacobs-university.de}{Denis Rochau} $\cdot$ \today} % Custom header text
\fancyfoot[RO,LE]{\thepage} % Custom footer text
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage[]{natbib}
\usepackage{tocloft}
\renewcommand*{\figureautorefname}{figure}
\def\stex{\texorpdfstring{\raisebox{-.5ex}S\kern-.5ex\TeX}{sTeX}\xspace}
\def\sTeX{\stex}

@@

@@

\subsection{Distance Between Robot and Reef}
\label{sec:distanceBetweenRobotAndReef}
\begin{wrapfigure}{l}{0.27\textwidth}
\vspace{-28pt}
  \begin{center}
  \fbox{
    \includegraphics[width=0.25 \textwidth]{assets/reefSideways.jpg}
    }
  \end{center}
\vspace{-20pt}
  \caption{Reef Sideways}
  \label{fig:reef}
\vspace{20pt}
\end{wrapfigure}

@@

\begin{wrapfigure}{c}{\textwidth}
\vspace{0pt}
  \begin{center}
  \fbox{
    \includegraphics[width=0.47 \textwidth]{assets/MapOnlyDistance}
    \includegraphics[width=0.4015 \textwidth]{assets/reefOriginalMappedComp}
    }
  \end{center}
\vspace{-20pt}
  \caption{Mapping using the Distance Algorithm}
  \label{fig:firstMapping}
\vspace{20pt}
\end{wrapfigure}

@@

\subsection{Improving the Value of scanDistance}
\label{sec:improvingValueOfScanDistance
}

In the previous section we have identified that one problem with our algorithm is that the value of \textit{scanDistance} might make us not explore areas because of spikes. While we need to make sure that the robot does not crash into anything, we still want to maximize what we can scan. Therefore, we will calculate the value \textit{scanDistance} not of the full field of vision of the robot but rather of a part of it that is as big as the robot.\\

\begin{wrapfigure}{l}{0.45\textwidth}
\vspace{-28pt}
  \begin{center}
  \fbox{
    \includegraphics[width=0.42 \textwidth]{assets/ReducedDistanceExplain.jpg}
    }
  \end{center}
\vspace{-20pt}
  \caption{Robot's Field of Vision}
  \label{fig:reducedDistanceExplain}
\vspace{20pt}
\end{wrapfigure}

Using the subpart of the field of vision of the robot that is as big as the robot ensures that we can move as close as possible to the reef while still not crashing into anything. This is illustrated in \autoref{fig:reducedDistanceExplain}. In \autoref{sec:distanceBetweenRobotAndReef}, the robot would take the whole field of vision illustrated by the outer yellow rectangle. In the new approach we would like to only use the smaller orange rectangle.\\

\begin{wrapfigure}{c}{\textwidth}
\vspace{-2pt}
\begin{lstlisting}[language=C++]
double DistanceFinder::imageCb(const sensor_msgs::ImageConstPtr& msg) {
	cv_bridge::CvImageConstPtr cv_ptr = getImage(msg, msg->encoding);
	double scanDistance = std::numeric_limits<double>::max();
	int startRobotFieldWidth = (fieldOfVisionWidth - robotWidth)/2;
	int endRobotFieldWidth = startRobotField + robotWidth;
	int startRobotFieldHeight = (fieldOfVisionHeight - robotHeight)/2;
	int endRobotFieldHeight = startRobotFieldHeight + robotWidth;

	for(int i = startRobotFieldWidth; i < endRobotFieldWidth; i++)
		for(int j = startRobotFieldHeight; j < endRobotFieldHeight; j++)
			if(cv_ptr->image.at<float>(i,j) < scanDistance)
				scanDistance = cv_ptr->image.at<float>(i,j);
	return scanDistance;
}
\end{lstlisting} 
\vspace{-38pt}
  \caption{Pseudocode Snippet to Show how to Control the Distance to the Cliff}
  \label{fig:codeReducedDistance}
  \vspace{60pt}
\end{wrapfigure}

The code in \autoref{fig:codeReducedDistance} will return the correct \textit{scanDistance} for the area of the robot robotField. This value will now be used in the code which we use to keep the correct distance to the reef (see \autoref{fig:codeDistance}). Using this improved version of the algorithm, the newly scanned map is better. The overall scanned map can be see in \autoref{fig:secondMapping}.\\

\begin{wrapfigure}{c}{\textwidth}
\vspace{0pt}
  \begin{center}
  \fbox{
    \includegraphics[width=0.47 \textwidth]{assets/ReducedDistanceFinding}
    \includegraphics[width=0.49 \textwidth]{assets/reefOriginal}
    }
  \end{center}
\vspace{-20pt}
  \caption{Mapping using the Distance Algorithm}
  \label{fig:secondMapping}
\vspace{20pt}
\end{wrapfigure}

When examining the map closer, we again look for holes in the map. Specifically, we will again look at the places whereh we found holes in the map before (see \autoref{fig:firstMappingProblems}). As can be seen in \autoref{fig:secondMappingProblems}, one hole is completely gone. The three other holes are slightly reduced but not yet fully mapped.\\

\begin{wrapfigure}{c}{\textwidth}
\vspace{-28pt}
  \begin{center}
  \fbox{
    \includegraphics[width=0.23 \textwidth]{assets/ReducedDistanceFindingHole1}
    \includegraphics[width=0.23 \textwidth]{assets/ReducedDistanceFindingHole2}
    \includegraphics[width=0.23 \textwidth]{assets/ReducedDistanceFindingHole3}
    \includegraphics[width=0.23 \textwidth]{assets/ReducedDistanceFindingHole4}
    }
  \end{center}
\vspace{-20pt}
  \caption{Mapping Problems using the Distance Algorithm}
  \label{fig:secondMappingProblems}
\vspace{20pt}
\end{wrapfigure}

\subsection{Scanning for Missing Data}

\ednote{more sensors or looking left and right}
